%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Devops/ Intermediate Software Developer} % Job title
    {Serato} % Organization
    {Auckland, New Zealand} % Location
    {Feb. 2020 - Current} % Date(s)
    {\renewcommand{\labelitemii}{\bullet}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item[] {\entrypositionstyle{Devops Engineer}
            \begin{itemize}[leftmargin=14pt,topsep=5pt] % Description(s) of tasks/responsibilities
                \itemsep0.3em
                \item {Designed and built \textbf{CICD pipelines} across multiple web applications with orchestration tools such as GitHub Workflow, Travis CI, and AWS CodePipelines. This eliminated 70\% of manual developer work, thus increasing productivity.}
                \item {Converted existing web applications into \textbf{Docker containers} for \textbf{AWS Elastic Container Service}, increasing both local development speed, shortening local setup time, and reducing cost of cloud service operation by 50\%.}
                \item {Accelerated web infrastructure deployments through the use of \textbf{Infrastructure as Code (IaC)}, specifically with \textbf{Cloudformation} and \textbf{AWS Cloud Development Kit} in \textbf{TypeScript}. Transforming from a deploy time of days, to just over an hour for our entire suite of microservices and cloud resources. }
                \item {Written scripts for a wide range of tasks in both \textbf{python} and \textbf{Javascipt}, some of which run on \textbf{AWS Lambda}.}
                \item {Performed initiatives to secure cloud platform with the use of the principle of least privilege. Giving developers, testers and deployers only the necessary permissions for their daily tasks.}
                \item {Mentored numerous junior developers on software development fundamentals, along with guiding them on well-architected cloud frameworks.}
                % \item {Worked with cloud services from Amazon such as \textbf{Cloudformation}, \textbf{Opsworks}, and \textbf{EC2}. With \textbf{Chef} configuration management. Using these tools to build and maintain a reliable and scalable infrastructure.}
              \end{itemize}}
        \item[] {\entrypositionstyle{Fullstack Developer}
            \begin{itemize}[leftmargin=14pt,topsep=5pt] % Description(s) of tasks/responsibilities
                \itemsep0.3em
                \item {Modularised monolithic web service architecture into microservices with RESTful APIs in \textbf{Node.js} and also \textbf{PHP}, using the \textbf{PHP Slim Framework}. Focusing on high quality object-oriented code. Using \textbf{Ngnix} for routing.}
                \item {Built unit tests and integration tests using \textbf{Jest}, \textbf{PHPUnit}, and \textbf{Postman}. Utilising test-driven development to ensure clean and concise code.}
                % \item {Developed dynamic and modular web components using \textbf{Vue.js}, \textbf{HTML/CSS/JavaScript/TypeScript}.}
                \item {Performed data sanitisation on customer PII, log tables, and legacy data across multiple \textbf{MySQL} databases using \textbf{SQL} scripts on \textbf{Amazon Aurora}. Reduced backup snapshot time by 80\%, increased testing throughput and reduced test environment provisioning time by 40\%.}
              \end{itemize}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer Intern} % Job title
    {Xero} % Organization
    {Auckland, New Zealand} % Location
    {Nov. 2017 - Feb. 2018} % Date(s)
    {
      \begin{cvitems2} % Description(s) of tasks/responsibilities
        \itemsep0.3em
        \item {Designed and created RESTful API in \textbf{C\#} using the \textbf{ASP.NET Core} framework, and documenting with Swagger.}
        \item {Developed dynamic web pages using \textbf{React/Redux} and \textbf{TypeScript}.}
        \item {Worked on continuous integration by using \textbf{TeamCity}, Artifactory, and Octopus.}
        \item {Built unit tests and integration tests using \textbf{Specflow}, \textbf{Jest}, and \textbf{Postman}.}
        \item {Oversaw application performance and errors through Pingdom, Sumologic, and Datadog.}
      \end{cvitems2}
    }

%---------------------------------------------------------
  \cventry
    {Technical Consultant} % Job title
    {Business Mechanix} % Organization
    {Auckland, New Zealand} % Location
    {Nov. 2016 - Nov. 2017} % Date(s)
    {
      \begin{cvitems2} % Description(s) of tasks/responsibilities
        \itemsep0.3em
        \item {Team lead on a cross-platform proof of concept \textbf{Xamarin} application, built using \textbf{C\#} and XAML.}
        \item {Utilised \textbf{Entity Framework} to build a ASP.NET MVC application.}
        \item {Hosted on Microsoft Server VM on premises, managed using remote desktop and ssh.}
        % \item {Developed RESTful APIs using \textbf{Entity Framework} and ASP.NET.}
      \end{cvitems2}
    }
    
%---------------------------------------------------------
\end{cventries}
